---
title: "Data Analysis for Job Positions"
output:
  word_document:
    toc: yes
  html_document:
    toc: yes
    theme: cosmo
    highlight: zenburn
date: "Dec 06 2020"
---
This file is used to EDA and analysis the data set from Github.

The aim of this project is to explore jobs and try to find the common vocabulary used in the job description.
Job type, company, title, location and description were analyzed below. For descriptions, texting manipulation was used to clean and dig the insight.
I used two data sets, which the larger one is from Kaggle and another one is from Github.The data set which is from Github Job and, specifically jobs for software developers，data science. Linkis are https://jobs.github.com/api.  The larger data set whcih is from Kaggle and jobs are from Australia.https://www.kaggle.com/vipulanand/jobs-data.
Due to there are not many jobs posted on the Github(around 150), then I downloaded a larger data set from Kaggle to show the reproducibility of my code.
I posted the larger data set in the repo as well. The code which is used to analysis are exactly same except the name of variable and attributes of job.
The shiny App show the content from Github.






# 0. Import Packages

```{r warning=FALSE, include=FALSE}
library(devtools)
library(tidyverse)
library(stringr) 
library(treemap)
library(plotly)
library(httr)
library(jsonlite)
library(wordcloud2)
library(RColorBrewer)
library(tm)
library(tokenizers)
library(tidytext)
library(plotly)
library(htmlwidgets)
library(webshot)
library(widgetframe)
library(gridExtra)
library(naniar)
library(knitr) 
library(tibble) 
```

# 1. Data Ingest
```{r warning=FALSE, paged.print=TRUE}
p1 = GET("https://jobs.github.com/positions.json?page=1")
p2 = GET("https://jobs.github.com/positions.json?page=2")
p3 = GET("https://jobs.github.com/positions.json?page=3")

p1 <- fromJSON(rawToChar(p1$content))
p2 <- fromJSON(rawToChar(p2$content))
p3 <- fromJSON(rawToChar(p3$content))

data <- rbind(p1, p2, p3)
names(data)
glimpse(data)
df <- data %>% select(id, type, company, location, title, description)
df <- as.data.frame(df)
df %>% head() %>% as.tibble() %>% view()

```

# 2. Exploratory Data Analysis

## 2.1 Missing Value

There is no missing existing in the data set.
```{r}
missing_col<-df %>% is.na() %>% colSums()
  missing_col <- data.frame(missing_col) %>% rownames_to_column()
  missing_df <- missing_col %>%
    mutate(Percentage_of_Missing=missing_col/nrow(df)*100) %>% arrange(desc(Percentage_of_Missing))
print(missing_df)
vis_miss(df)
```

## 2.2 Summary for Type, Company, Title and Location
There are two types of job, i.e. Contract and Full Time. There are nearly 150 fulltime jobs compared with Contract's.
Top 5 companies listed IT positions are Genpact, Gemini, Raycast, InnoGames Gmbh, and Axios.
Top 5 titles listed on Github are Senior Software Engineer, DevOps Engineer, Lead Consultant-UI with React, Node JS, Full Stack Engineer and Developer Advocate.
Top 5 work locations are Remote, Berlin, Bangalore and Hamberg.
```{r, fig.width=18, fig.height=10}
df %>% summarise(distinct_type=n_distinct(type), distinct_company=n_distinct(company),distinct_title=n_distinct(title), distinct_lication=n_distinct(location))



type_bar <- ggplot(df, aes(x=type)) +
            geom_bar(fill="green") +     
            theme(axis.title.x = element_blank(), axis.title.y = element_blank(),
                  legend.position = "none", plot.title = element_text(hjust = 0.5, size=25), text = element_text(size=20)) + ggtitle("Type")
company_bar <- ggplot(df %>% group_by(company) %>% summarise(count_company=n()) %>% arrange(-count_company) %>% head(5), aes(x=reorder(company, count_company), y=count_company)) +
            geom_bar(stat="identity", fill="darkred") +coord_flip()+
            theme(axis.title.x = element_blank(), axis.title.y = element_blank(),
                  legend.position = "none", plot.title = element_text(hjust = 0.5, size=25), text = element_text(size=20)) + ggtitle("Company")
title_bar <- ggplot(df %>% group_by(title) %>% summarise(count_title=n()) %>% arrange(-count_title) %>% head(5), aes(x=reorder(title, count_title), y=count_title)) +
            geom_bar(stat="identity", fill="purple") +coord_flip()+
            theme(axis.title.x = element_blank(), axis.title.y = element_blank(),
                  legend.position = "none", plot.title = element_text(hjust = 0.5, size=25), text = element_text(size=20)) + ggtitle("Title")

location_bar <- ggplot(df %>% group_by(location) %>% summarise(count_location=n()) %>% arrange(-count_location) %>% head(5), aes(x=reorder(location, count_location), y=count_location))+
           geom_bar(stat="identity", fill="steelblue") + coord_flip()+
           theme(axis.title.x = element_blank(), axis.title.y = element_blank(),
                  legend.position = "none", plot.title = element_text(hjust = 0.5, size=25), text = element_text(size=20)) + ggtitle("Location")

type_bar
company_bar
title_bar
location_bar
```

## 2.3 Description
### 2.3.1 Common words
First, check the top 20 common words in job description. From plot below, there are some html decoration words which are from websites existing. Besides those html format words, strong, work, experience, data and etc. are the most common words in the descriptions.
```{r warning=FALSE}
STOPWORDS <- stopwords(kind = "en")
generate_cm_wd <- function(ccc){
  words <- paste(ccc, collapse = " ") 
  words <- tokenize_words(words)
  tab <- table(words[[1]])
  tab <- data_frame(word = names(tab), count = as.numeric(tab))
  tab <- tab %>% filter(!word %in% STOPWORDS) %>% arrange(desc(count)) %>% head(20)
  return(tab)
}

df_cm_wd <- generate_cm_wd(df$description)
df_cmwd_bar<-ggplot(data=df_cm_wd, aes(x=word, y=count, fill=count)) +
  geom_bar(stat="identity")+coord_flip()+
  scale_fill_continuous(low="blue", high="green")+
  theme_minimal() +theme(axis.title.y = element_blank(),
                          legend.position = "none")
df_cmwd_bar

```

### 2.3.2 Number of words in each job description and Average length for each job description
Most job descriptions contain between 250 and 800 words. The distribution is little bit right skewed. Job descriptions with more than 1000 words are less than 5.

Average words in the description is right skewed

```{r}
df <- df %>% mutate(text_words = sapply(strsplit(df$description, " "), length))
df <- df %>% mutate(text_len = str_count(description))
df <- df %>% mutate(text_avg_words = text_len/text_words)

# Number of words
num_words <- ggplot(df, aes(x=text_words)) +
            geom_histogram(fill="lightblue") +     
            theme(legend.position = "none", plot.title = element_text(size = 20, face = "bold", hjust = 0.5), text = element_text(size=12)) + ggtitle("Number of Words")
# Average words
ave_words <- ggplot(df, aes(x=text_avg_words)) +
            geom_density(fill="lightblue") +     
            theme(legend.position = "none", plot.title = element_text(size = 20, face = "bold", hjust = 0.5), text = element_text(size=12)) + ggtitle("Average Length of Words")


num_words
ave_words
```

### 2.3.3 Clean text and word cloud
```{r}
stopwords_regex = paste(stopwords('en'), collapse = '\\b|\\b')
stopwords_regex = paste0('\\b', stopwords_regex, '\\b')
df$description<- str_replace_all(df$description, stopwords_regex, '')
df$description <- str_replace_all(df$description, regex('[:punct:]'), "")
df$description <- str_replace_all(df$description, regex('[:digit:]'), "")
df$description <- str_replace_all(df$description, regex('<p>'), " ")
df$description <- str_replace_all(df$description, regex('und'), " ")
df$description <- str_replace_all(df$description, regex('</p>'), " ")
df$description <- str_replace_all(df$description, regex('will'), " ")
df$description <- str_replace_all(df$description, regex('you'), "")
df$description <- str_replace_all(df$description, regex('the'), "")
df$description <- str_to_lower(df$description, locale = 'en')
description <- Corpus(VectorSource(df %>% select(description)))
desp <- description %>% 
    tm_map(removeNumbers) %>%
    tm_map(removePunctuation) %>%
    tm_map(removeWords, stopwords("english")) %>% 
    tm_map(stripWhitespace)
desp <- tm_map(desp, content_transformer(tolower))

desp <- TermDocumentMatrix(desp) 
matrix <- as.matrix(desp) 
words <- sort(rowSums(matrix),decreasing=TRUE) 
pre_words <- data.frame(word = names(words),freq=words)


clean_desp <- wordcloud2(pre_words, size=1.6, color='random-dark')+ WCtheme(1)
clean_desp

ggplot(pre_words %>% head(10), aes(x=reorder(word, freq), y=freq)) +
                    geom_bar(stat="identity", fill="steelblue")+coord_flip()+
                    theme(axis.title.x = element_blank(), axis.title.y = element_blank(),
                          legend.position = "none", plot.title = element_text(hjust = 0.5, size=25), text = element_text(size=20))+ ggtitle("Count of Words for Description")

```
#Discussion:
From the exploration of data set of software engineer from github, it is clear that:" team, experience, data" are top 3 common words.
Although the categories of job are different in those two data sets, the two of top 3 common words are overlapped, which are "team" and "experience"!
Based on that I think I will add more words which are related to team and experience such as leadership, teamwork, group work on my resume.